\documentclass[russian]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{amsmath, amssymb}
\usepackage{esint}
\usepackage{babel}
\makeatletter
\makeatother

\begin{document}

living in a big city is a strange thing. % 9 
on one hand there are many opportunities to work or entertain yourself. % 12 21
there are many shops and other services, you can find there almost everything you want. % 15 36
threre are many people that you can find some common interests with. % 12 48
it's a great place to do business, or just to find some place to work. % 16 64
on the other hand all that stuff fades as you leave downtown. %12 76
you get grey boring sleeping areas with boring people that are always in a hurry and absolutely nothing to do there. % 21 97
add to it constant traffic jams, drunk chavs, and total absence of civilisation and you will get a hell you'll never want to live in. % 26 123
you have to go downtown for every single thing you need. %11 134
obviously there are some rare exceptions from that rule, but i have never seen them here, in russia. %18 152
the other contrary case is some small towns, where you get almost the same problems like in that boring sleeping areas. %21 173
except for having some big cities downtown nearby. %8 181

however there are special towns like academ. % 7
it's like a small big city, but without all that nasty suburbs and common city problems. % 17 24
you can reach almost everything on foot and there is actually what to reach. % 14 38
lots of shops for any type of thing you want. % 10 48
cinema, theatre and several clubs. % 5 53
finding a bar to rest after a hard work day is also not a problem. % 15 68
as is finding the work itself - here is a great variety of companies for any taste. % 16 84

% 265

the other big advantage here is the NSU. % 8
as you learn there you get many career opportunities and, the most valuable - lots of new friends. % 17 25
as a result everyone knows each other here. % 8 33
if you see someone in the street he's either your friend or one of you friends' friend. % 18 51
you cannot ever be that social in a big city. % 10 61

% 326

\end{document}

